---
title: "Coursework"
author: "Dara, Guedem"
date: 2022-11-26T21:13:14-05:00
categories: ["R"]
#tags: ["R Markdown", "treemap", "summary"]
widget: coursework
weight: 15
---

```{r setup, include=FALSE}
require("knitr")
knitr::opts_knit$set (root.dir = "C:/Users/gd129/Desktop/Job Applications/My Data Analytic Portfolio/Website 2/Course work")
```

## `Dara Guedem's Coursework Data`

To give a summary of some of the graduate courses that I have taken over the years, I created a data set of 29 courses and five variables where: 

  - year = academic year
  - season = Spring or Fall semester, 
  - FieldOfStudy = field of study, 
  - course = course department number and title, 
  - credits = the number of credits per course (1-10), and 
  - software = software used in a course. 
  
The graph below shows some of the graduate level courses that I completed from the University of Montana; MA in Economics (2012 - 2015) and MSBA (2017 - 2018). I've also resourced myself through different books and online tutorials (from YouTube) post graduation. Lately, I have completed some online courses via Udemy.



```{r load dataset, echo=FALSE}
#load my coursework data
coursework <- read.csv("coursework.csv")
coursework$course <- factor(coursework$course)              #course dpt & title
coursework$FieldOfStudy <- factor(coursework$FieldOfStudy)  #field of study
coursework$software <- factor(coursework$software)          #software

library(treemap)

treemap(coursework,
        index = c("FieldOfStudy", "course", "software"),    #Field of study, course, and software.
        vSize = "credits",                                  #course credits
        vColor =  "FieldOfStudy",
        title = "Dara Guedem's Relevant Coursework by Field of Study and Software Usage",
        align.labels = list(
          c("left", "bottom"), 
          c("center", "center")
        )
      )
```

Note: ECNS 599 is a 10 credits course split into 2 semesters (Fall 2014 and Spring 2015). 

## `Frequency of Software Usage`
Table of frequency of software used in the different courses that I completed over the years. 

```{r, echo=TRUE}
library(dplyr)

freq_by_course <- coursework %>%
                    group_by(software) %>%
                    summarise(n = n(), .groups = 'drop') %>%
                    mutate(Frequency = paste0(round(100 * n/sum(n), 0), '%'))
freq_by_course
```

Note: I've used STATA the longest because I started using it as an undergraduate student at the UM. 
